### 2020-02-08 cv_models.tex
updated cv section

\paragraph{Layer Analysis: Correlation Flow in CV Models.}
We can learn much more about a pretrained model by going beyond average values to examining quality metrics for each layer weight matrix, $\mathbf{W}$, as a function of depth (or layer id).  % in the network. 
%The most interesting results are seen when we 
For example, we can 
plot (just) the PL exponent, $\alpha$,%
\footnote{That is, here we consider just $\alpha$ for each layer, i.e., not $\hat{\alpha}$ or $\Vert\mathbf{W}\Vert^{\alpha}_{\alpha}$.} 
as a function of depth.
%
See Figure~\ref{fig:3models-alpha-layers}, which plots $\alpha$ for each layer (the first layer corresponds to data, the last layer to labels) for the least accurate (shallowest) and most accurate (deepest) model in each of the VGG (without BatchNormalization), ResNet-1K, and DenseNet series.
(Again, much more detailed set of plots is available at \cite{XXX-WEB-LINK}; but note that the corresponding layer-wise plots for Frobenius and Spectral norms are much less interesting than the results we present here.)

@@

}    \subfigure[ DenseNet ]{
        \includegraphics[width=4.0cm]{img/resnet_alpha_overlaid_depth.png} 
        \label{fig:resnet_alpha_overlaid_depth}
    }
    \caption{Correlation Flow: Power Law exponent $\alpha$ versus layer id, for the least and the most accurate
      models in VGG (a), ResNet (b), and DenseNet (c) series (VGG without BatchNorm, and the Y axes on each plot are different.)  
             Figure (d) displays the ResNet models (b), zoomed in to $alpha\in[1,5]$, and with the layer ids overlaid on the X-axis, to
             allow a more detailed analysis for the most strongly correlated layers.
             Notuece that ResNet152 exhibits different and much more stable behavior across layers
             This contrasts with how both VGG models gradually worsen in deeper layers and how the DenseNet models are much more erratic.  
            }
    \label{fig:3models-alpha-layers}
\end{figure}

@@

Recall the differences---in particular, the number of residual connections---between the VGG, ResNet, and DenseNet architectures.
VGG, while a fine model in many ways, was limited by needing massive FC layers at the end of the model, requiring significant memory and computational resources, and it's poor conditioning led to problems with vanishing gradients.  
The empirical manifestations of this (on weight matrices) are that fitted $\alpha$ values get much worse for deeper layers.
ResNet greatly improved on VGG by introducing residual connections, allowing for greater accurary with far fewer parameters.
(Indeed, ResNet models of up to 1000 layers have been trained.) 
We conjuecture that the effeciency and effectivness of ResNet is reflected in the smaller and more stable $\alpha\sim 2.0$, across nearly all layers, indicating that the inner layers are very well correlated and strongly optimized.
This should also be contrasted with the DenseNet model, which contains many connections between every layer.
Our results (large $\alpha$, meaning they even a HT model is probably a poor fit) suggest that DenseNet has too many connections, diluting high quality interactions across layers, and leaving many layers very poorly optimized.

@@

%\paragraph{Layer Analysis: Behavior on Less Thoroughy Studied CV Models.}
\paragraph{Layer Analysis: Differences Between PL Metrics and Norm Metrics.}

@@

\begin{figure}[t]
   \centering
   \subfigure[$\lambda_{max}$ for ResNet20 layers]{
      %\includegraphics[scale=0.14]{img/resnet4d_maxev.png}
      \includegraphics[width=4.0cm]{img/resnet4d_maxev.png}
      %\includegraphics[width=4.5cm]{img/resnet4d_maxev.png}
      \label{fig:resnet204Dalpha}
   }
   %\qquad
   \subfigure[$\alpha$ for ResNet20 layers]{
      %\includegraphics[scale=0.14]{img/resnet4d_alphas.png}
      \includegraphics[width=4.0cm]{img/resnet4d_alphas.png}
      %\includegraphics[width=4.5cm]{img/resnet4d_alphas.png}
      \label{fig:resnet204Dmaxev}
   }
   \caption{Layer Analysis.
            ResNet20, distilled with Group Regularization, as implemented in the \texttt{distiller} (4D\_regularized\_5Lremoved) pre-trained models.  
            Spectral Norm, $\lambda_{max}$, and, PL exponent, $\alpha$, for individual layer, versus layer id, for both between baseline (before distillation, shown in green) and fine-tuned (after distillation, shown in red) pre-trained models. 
           }
   \label{fig:resnet204D5L}
\end{figure}

>>>>

\paragraph{Correlation Flow}
We can learn much more about a pretrained model by going beyond average values to examining quality metrics for each layer weight matrix, $\mathbf{W}$, as a function of depth (or layer id).  % in the network. 
%The most interesting results are seen when we 
For example, we can 
plot (just) the PL exponent, $\alpha$,%
\footnote{That is, here we consider just $\alpha$ for each layer, i.e., not $\hat{\alpha}$ or $\Vert\mathbf{W}\Vert^{\alpha}_{\alpha}$.} 
as a function of depth.
%
See Figure~\ref{fig:3models-alpha-layers}, which plots $\alpha$ for each layer (the first layer corresponds to data, the last layer to labels) for the least accurate (shallowest) and most accurate (deepest) model in each of the VGG (without BatchNormalization), ResNet-1K, and DenseNet series.
(Again, much more detailed set of plots is available at \cite{XXX-WEB-LINK}; but note that the corresponding layer-wise plots for Frobenius and Spectral norms are much less interesting than the results we present here.)

@@

}    \subfigure[ ResNet (overlaid) ]{
        \includegraphics[width=4.0cm]{img/resnet_alpha_overlaid_depth.png} 
        \label{fig:resnet_alpha_overlaid_depth}
    }
    \caption{Correlation Flow: Power Law exponent $\alpha$ versus layer id, for the least and the most accurate
      models in VGG (a), ResNet (b), and DenseNet (c) series (VGG without BatchNorm, and the Y axes on each plot are different.)  
             Figure (d) displays the ResNet models (b), zoomed in to $alpha\in[1,5]$, and with the layer ids overlaid on the X-axis, to
             allow a more detailed analysis for the most strongly correlated layers.
             Notice that ResNet152 exhibits different and much more stable behavior across layers
             This contrasts with how both VGG models gradually worsen in deeper layers and how the DenseNet models are much more erratic.  
            }
    \label{fig:3models-alpha-layers}
\end{figure}

@@

%Recall the differences---in particular, the number of residual connections---between the VGG, ResNet, and DenseNet architectures.
%VGG, while a fine model in many ways, was limited by needing massive FC layers at the end of the model, requiring significant memory and computational resources, and it's poor conditioning led to problems with vanishing gradients.  
%The empirical manifestations of this (on weight matrices) are that fitted $\alpha$ values get much worse for deeper layers.
\ncyan{We can interpret these observations by recalling the architectural differences between the VGG, ResNet, and DenseNet architectures,
and, in particular, the number of of residual connections. VGG resembles the  traditional convolutional architectures,
such as LeNet5, and consists of several [Conv2D-Maxpool-ReLu] blocks, followed by 3 large Fully Connected (FC) layers.
ResNet greatly improved on VGG by replacing the large FC layers, shrinking the Conv2D blocks, and introducing \emph{residual connections}.
This optimized approach allows for greater accurary with far fewer parameters (and GPU memory requirements), and
ResNet models of up to 1000 layers have been trained.\cite{resnet1000}.}
We conjuecture that the effeciency and effectivness of ResNet is reflected in the smaller and more stable $\alpha\sim 2.0$, across nearly all layers, indicating that the inner layers are very well correlated and strongly optimized.
Contrast this with the DenseNet models, which contains many connections between every layer.
Our results (large $\alpha$, meaning they even a HT model is probably a poor fit) suggest that DenseNet has too many connections, diluting high quality interactions across layers, and leaving many layers very poorly optimized.

@@

%\paragraph{Layer Analysis: Behavior on Less Thoroughy Studied CV Models.}
\paragraph{Corraltion Flow: PL vs. Norm Metrics.}

@@

\begin{figure}[t]
   \centering
   \subfigure[$\lambda_{max}$ for ResNet20 layers]{
      %\includegraphics[scale=0.14]{img/resnet4d_maxev.png}
      \includegraphics[width=4.0cm]{img/resnet4d_maxev.png}
      %\includegraphics[width=4.5cm]{img/resnet4d_maxev.png}
      \label{fig:resnet204Dalpha}
   }
   %\qquad
   \subfigure[$\alpha$ for ResNet20 layers]{
      %\includegraphics[scale=0.14]{img/resnet4d_alphas.png}
      \includegraphics[width=4.0cm]{img/resnet4d_alphas.png}
      %\includegraphics[width=4.5cm]{img/resnet4d_alphas.png}
      \label{fig:resnet204Dmaxev}
   }
   \caption{Correlation Flow.
            ResNet20, distilled with Group Regularization, as implemented in the \texttt{distiller} (4D\_regularized\_5Lremoved) pre-trained models.  
            Spectral Norm, $\log\lambda_{max}$, and, PL exponent, $\alpha$, for individual layer, versus layer id, for both baseline (before distillation, green) and finetuned (after distillation, red) pre-trained models. 
           }
   \label{fig:resnet204D5L}
\end{figure}
